\Large \bf 6.829 Final Project: A comparison of bit-rate selection algorithms

### 2013-05-16 paper/paper.tex
tweak

We implemented SampleRate as outlined in John Bicket's Master's thesis~\cite{samplerate}. This implementation is slightly different from how it was implemented in the MadWifi kernel driver. The primary difference is that the kernel implementatiion uses a EWMA instead of a 10 second window. The thesis implementation computes success probabilities based on a 10-second sliding window. It would be worth looking at the performance of EWMA-based SampleRate in the future.  Our implementation, \texttt{samplerate.py} contains \texttt{ApplyRate()}, \texttt{ProcessFeedback()} and  \texttt{RemoveStaleResults()}, as well as a few helper functions and data structures for tracking rate statistics.

>>>>

We implemented SampleRate as outlined in John Bicket's Master's thesis~\cite{samplerate}. This implementation is slightly different from how it was implemented in the MadWifi kernel driver. The primary difference is that the kernel implementatiion uses a EWMA, while the thesis implementation computes average transmission times based on a 10-second sliding window. It would be worth looking at the performance of EWMA-based SampleRate in the future.  Our implementation, \texttt{samplerate.py} contains \texttt{ApplyRate()}, \texttt{ProcessFeedback()} and  \texttt{RemoveStaleResults()}, as well as a few helper functions and data structures for tracking rate statistics.
